Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife

### 2024-03-26 analysis/paper/paper.Rmd
change name to weightRaster, remove no longer needed finResProject fun, make sure runTimes are not lost when re-running metric calcs

# re-run projections for just the small area with different parameters
mstProj <- projectAll(tsbs = tsb, paramTable = paramTable,
                      costSurface = tsaCost,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"))

ilcpProj <- projectAll(tsbs = tsb,
                      paramTable = paramTable %>% 
                        filter(sampleType == "regular") %>% 
                        mutate(method = "ilcp"),
                      costSurface = tsaCost,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"))

>>>>

# re-run projections for just the small area with different parameters
mstProj <- projectAll(tsbs = tsb, paramTable = paramTable,
                      weightRaster = tsaCost,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"),
                      roadsInWeight = F)

ilcpProj <- projectAll(tsbs = tsb,
                      paramTable = paramTable %>% 
                        filter(sampleType == "regular") %>% 
                        mutate(method = "ilcp"),
                      weightRaster = tsaCost,
                      cutblocks = cutblocks,
                      existingRoads = exRoads,
                      fileLocation = here(data_path_drvd, "..", "for_fig"),
                      roadsInWeight = F)
